Graph Topological Aspects of Granger Causal Network Learning

### 2019-06-30 paper/paper.tex
Slight figure rearranging.

\begin{figure}
  \centering
  \caption{PWGC Compared Against AdaLASSO \cite{adaptive_lasso_zou2006}}
  \label{fig:simulation_results}

  \begin{subfigure}[b]{0.45\textwidth}
    \caption{PWGC vs adaLASSO (SCG)}
    \label{fig:simulation_results_comparison1}
    \includegraphics[width=\linewidth]{new_lasso_comparison_scg_simulation.pdf}
    % \missingfigure{}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \caption{PWGC vs adaLASSO (DAG, $q = \frac{2}{n}$)}
    \label{fig:simulation_results_comparison2}
    \includegraphics[width=\linewidth]{new_lasso_comparison_dag_simulation.pdf}
    % \missingfigure{}
  \end{subfigure}

  {\scriptsize Comparison of PWGC and LASSO for $\VAR(p)$ model
    estimation.  We make comparisons against both the MCC and the
    relative log mean-squared prediction error
    $\frac{\ln\tr \widehat{\Sigma}_v}{\ln\tr \Sigma_v}$.  Results
    in Figure \ref{fig:simulation_results_comparison1} are for systems
    guaranteed to satisfy the assumptions required for Theorem
    \ref{thm:scg_recovery}.  Figure
    \ref{fig:simulation_results_comparison2} provides results for
    systems which do not guarantee the assumptions of Theorem
    \ref{thm:scg_recovery}, though the graph has a similar level of
    sparsity.}
\end{figure}

>>>>

\begin{figure}
  \centering
  \caption{PWGC Compared Against AdaLASSO \cite{adaptive_lasso_zou2006} (SCG)}
  \label{fig:simulation_results_comparison1}
  \includegraphics[width=0.95\textwidth]{new_lasso_comparison_scg_simulation.pdf}

  {\scriptsize Comparison of PWGC and LASSO for $\VAR(p)$ model
    estimation.  We make comparisons against both the MCC and the
    relative log mean-squared prediction error
    $\frac{\ln\tr \widehat{\Sigma}_v}{\ln\tr \Sigma_v}$.  Results
    in Figure \ref{fig:simulation_results_comparison1} are for systems
    guaranteed to satisfy the assumptions required for Theorem
    \ref{thm:scg_recovery}.}
\end{figure}

\begin{figure}
  \caption{PWGC vs adaLASSO (DAG, $q = \frac{2}{n}$)}
  \label{fig:simulation_results_comparison2}
  \includegraphics[width=0.95\textwidth]{new_lasso_comparison_dag_simulation.pdf}
  {\scriptsize Figure \ref{fig:simulation_results_comparison2}
    provides results for systems which do not guarantee the
    assumptions of Theorem \ref{thm:scg_recovery}, though the graph
    has a similar level of sparsity.}
\end{figure}
